Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Methodology and evaluation, summary

@@

The primary study of the rate of collision between roads and other features, will serve to obtain the following three metrics:

>>>>

In this chapter we will look in details at the evaluation metrics that this project served to obtain, and how they relate to the eventual collision analysis.
For the geodata precision study specifically, we will look in detail at how geodata is qualifyied in general, by examining van Oorts quality criteria.
We will also present how van Oorts critera will be used in the context of this project.
See section 4 for a detailed technical implementation overview that presents how the relevant metrics were obtained during the statistics collection process.
For the resulting metrics that were obtained, see section 5.

@@

The primary study of the rate of collision between roads and other features will serve to obtain the following three metrics:
